% add \usepackage{seqsplit} to your preamble 
\seqsplit{https://www.theworldavatar.com/kg/ontogreenspace/GreenspaceEnd~{$\sqsubseteq$}~http://ies.data.gov.uk/ontology/ies4#BoundingState} \\
\seqsplit{https://www.theworldavatar.com/kg/ontogreenspace/GreenspaceEnd~{$\sqsubseteq$}~{$\forall$}~http://ies.data.gov.uk/ontology/ies4#isEndOf.https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{https://www.theworldavatar.com/kg/ontogreenspace/GreenspaceStart~{$\sqsubseteq$}~http://ies.data.gov.uk/ontology/ies4#BoundingState} \\
\seqsplit{https://www.theworldavatar.com/kg/ontogreenspace/GreenspaceStart~{$\sqsubseteq$}~{$\forall$}~http://ies.data.gov.uk/ontology/ies4#isStartOf.https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\exists$}~http://ies.data.gov.uk/ontology/ies4#inPeriod.{$\top$}~{$\sqsubseteq$}~(https://www.theworldavatar.com/kg/ontogreenspace/GreenspaceEnd~{$\sqcup$}~https://www.theworldavatar.com/kg/ontogreenspace/GreenspaceStart)} \\
\seqsplit{{$\exists$}~http://ies.data.gov.uk/ontology/ies4#isEndOf.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/GreenspaceEnd} \\
\seqsplit{{$\exists$}~http://ies.data.gov.uk/ontology/ies4#isStartOf.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/GreenspaceStart} \\
\seqsplit{{$\exists$}~https://www.theworldavatar.com/kg/ontogreenspace/hasReferenceToGreenspaceSite.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/AccessPoint} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~http://ies.data.gov.uk/ontology/ies4#inPeriod.http://ies.data.gov.uk/ontology/ies4#ParticularPeriod} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~http://ies.data.gov.uk/ontology/ies4#isEndOf.https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~http://ies.data.gov.uk/ontology/ies4#isStartOf.https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~https://www.theworldavatar.com/kg/ontogreenspace/hasReferenceToGreenspaceSite.https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\exists$}~http://ies.data.gov.uk/ontology/ies4#iso8601PeriodRepresentation.{$\top$}~{$\sqsubseteq$}~http://ies.data.gov.uk/ontology/ies4#ParticularPeriod} \\
\seqsplit{{$\exists$}~http://www.opengis.net/ont/geosparql#asWKT.{$\top$}~{$\sqsubseteq$}~(https://www.theworldavatar.com/kg/ontogreenspace/AccessPoint~{$\sqcup$}~https://www.theworldavatar.com/kg/ontogreenspace/Greenspace)} \\
\seqsplit{{$\exists$}~https://www.theworldavatar.com/kg/ontogreenspace/hasAccessType.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/AccessPoint} \\
\seqsplit{{$\exists$}~https://www.theworldavatar.com/kg/ontogreenspace/hasFirstAlternativeName.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\exists$}~https://www.theworldavatar.com/kg/ontogreenspace/hasFunction.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\exists$}~https://www.theworldavatar.com/kg/ontogreenspace/hasGID.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\exists$}~https://www.theworldavatar.com/kg/ontogreenspace/hasID.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\exists$}~https://www.theworldavatar.com/kg/ontogreenspace/hasName.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\exists$}~https://www.theworldavatar.com/kg/ontogreenspace/hasSecondAlternativeName.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\exists$}~https://www.theworldavatar.com/kg/ontogreenspace/hasThirdAlternativeName.{$\top$}~{$\sqsubseteq$}~https://www.theworldavatar.com/kg/ontogreenspace/Greenspace} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~http://ies.data.gov.uk/ontology/ies4#iso8601PeriodRepresentation.xsd:anyURI} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~http://www.opengis.net/ont/geosparql#asWKT.http://www.opengis.net/ont/geosparql#wktLiteral} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~https://www.theworldavatar.com/kg/ontogreenspace/hasAccessType.xsd:string} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~https://www.theworldavatar.com/kg/ontogreenspace/hasFirstAlternativeName.xsd:string} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~https://www.theworldavatar.com/kg/ontogreenspace/hasFunction.xsd:string} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~https://www.theworldavatar.com/kg/ontogreenspace/hasGID.xsd:integer} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~https://www.theworldavatar.com/kg/ontogreenspace/hasID.xsd:string} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~https://www.theworldavatar.com/kg/ontogreenspace/hasName.xsd:string} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~https://www.theworldavatar.com/kg/ontogreenspace/hasSecondAlternativeName.xsd:string} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~https://www.theworldavatar.com/kg/ontogreenspace/hasThirdAlternativeName.xsd:string} \\
